---
title: "Assignment-B1"
output: md_document
date: "2023-10-31"
---

```{r}
library(tidyverse)
library(testthat)
library(datateachr)
set.seed(2023)
```

# Exercise 1: Make a Function (25 points)

In this exercise, you'll be making a function and fortifying it. The function need not be complicated. The function need not be "serious", but shouldn't be nonsense.

```{r}
df_var <- function(df) {
  # Check if df is empty or not
  if(is_empty(df)) {return("Please use a non-empty dataframe.")}
  output <- c()
  for(i in 1:ncol(df)){
    # Verify numeric values in the dataframe 
    if(!is.numeric(unlist(df[,i]))) {
      return("You have a non numeric column, please select a dataframe with all numeric column")
    }
    if(is.numeric(unlist(df[,i]))) {
    output[i] <- var(df[,i])
    }
  }
return(output)
}
```

# Exercise 2: Document your Function (20 points)

In the same code chunk where you made your function, document the
function using roxygen2 tags. Be sure to include:

```{r}
#' df_var
#'
#' @description A function that calculates the variance for each numeric columns in a dataframe. 
#' @param df The input dataframe that you want to find the variance of each column. 
#' @return It returns a vector of variances corresponds to each numeric column in the dataframe. 
df_var <- function(df) {
  # Check if df is empty or not
  if(is_empty(df)) {return("Please use a non-empty dataframe.")}
  output <- c()
  for(i in 1:ncol(df)){
    # Verify numeric values in the dataframe 
    if(!is.numeric(unlist(df[,i]))) {
      return("You have a non numeric column, please select a dataframe with all numeric column")
    }
    if(is.numeric(unlist(df[,i]))) {
    output[i] <- var(df[,i])
    }
  }
return(output)
}
```

# Exercise 3: Include examples (15 points)

Demonstrate the usage of your function with a few examples. Use one or
more new code chunks, describing what you're doing.

```{r}
# Here we test a empty dataframe
df <- data.frame()
df_var(df)
```

```{r}
# Here we test the cancer data from dataeachr package, it contains a non-numeric column.
df_var(cancer_sample)
```
```{r}
# Here we remove the non-numeric column from the cancer data above and test the new data.
new_cancer <- cancer_sample %>%
  select(-diagnosis)
ex <- df_var(new_cancer)
ex
```
# Exercise 4: Test the Function (25 points)

Running examples is a good way of checking by-eye whether your function
is working as expected. But, having a formal "yes or no" check is useful
when you move on to other parts of your analysis.

Write formal tests for your function. You should use at least three
non-redundant uses of an `expect_()` function from the `testthat`
package, and they should be contained in a `test_that()` function (or
more than one). They should all pass.

```{r}
test_that("Invalid groupby_names", {
  # Should get an error for a non dataframe input
  expect_error(df_var(rnorm(10)))
  # Checking if the answer match
  expect_equal(df_var(new_cancer), ex)
  # Check if the answer is numeric
  expect_true(is.numeric(ex))
  # Check if the answer is correct
  expect_equal(length(df_var(new_cancer)),31)
          })
```





